A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-06-02 LensingPaper_draft_v4.01.tex
Started shortening the Lensing theory section.

\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM distribution of a massive galaxy. This would require in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}

@@

The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
\end{equation}
 According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.

@@

%============================================
\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}
%============================================

@@

%--------------------------------------------
We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}). The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.

>>>>

\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive galaxy. This would require in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}

@@

\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
\end{equation}
 According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}

@@

%============================================
\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \OLD{\eqref{eq:timedelay}}\NEW{(63) in \citet{1996astro.ph..6001N}}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}
%============================================

@@

%--------------------------------------------
We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}). The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface \NEW{(see \S 3.3.1 in \citet{1996astro.ph..6001N}).  Fermat's principle states that the image positions are observed at the extrema of the time delay surface. And even though}\OLD{. This demonstrates that, although} we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
